---
title: "Problem3"
author: "Devin Etcitty"
date: "4/25/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(tidyverse)
library(scales)
library(igraph)
library(plyr)
library(reshape2)
```

#### Read in undweighted10.dat
First, read in the edge list for 2010 from the undweighted10.dat file

```{r}
#setwd("~/columbia/APMA4990/msd-homework/homework/homework_3/problem_3")
setwd("~/Documents/Columbia/msd-apam4990/msd2017/homework/homework_3/problem_3")
year2010 <- read.delim("undweighted10.dat", header = FALSE, sep = ' ')
colnames(year2010) <- c('userID1', 'userID2', 'num_email')

```


Make a plot of the distribution of edge weights for the entire network
Use a log-log scale and comment on the result. What does it tell you about the distribution of tie strength?

```{r}
count_df <- year2010 %>% 
  count('num_email')

#count_df

```

# Graph

```{r}
ggplot(count_df, aes(x=num_email, y=freq)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()


```

```{r}

```


```{r}
ggplot(count_df, aes(x=freq, y =num_email)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

```




```{r}
power2 <- 2^(0:10)
power2 <- append(power2, 0, 0)
power2
```




```{r}
final_df  <- data.frame(nodes=integer(),
                 edges=integer(), 
                 num_connected_components=integer(), 
                 percent_of_nodes_in_max_component=double(),
                 ave_path_distance=double()) 

for(i in power2) {
  df <- year2010 %>%
    filter(num_email > i)
  
  g <- graph_from_data_frame(df, directed = FALSE, vertices = NULL)
  
  nodes <- gorder(g)
  edges <- gsize(g)
  
  num_connect_comps <- no.clusters(g)
  clus <- clusters(g)

  test <- groups(clus)
  
  d <- adply(test, '1', length)

  max_num_nodes_comp <- max(d$V1)
  
  percent_connect_comp <- max_num_nodes_comp / nodes
  
  avg_distance <- mean_distance(g)

  results = c(nodes, edges, num_connect_comps, percent_connect_comp, avg_distance)
  
  final_df <- rbind(final_df, i = results)

}


```



```{r}
colnames(final_df) <- c("nodes", "edges", "num_connect_comps", 
                     "percent_connect_comp", "avg_distance")
```


```{r}
final_df <- cbind(power2, final_df)
```

```{r}
final_df
```


```{r}
ggplot(final_df, aes(x=power2, y=nodes)) +
  scale_x_log10() +
  geom_point() +
  labs(title = "Number of Nodes")
```

The number of nodes decreases as the threshold value increases.

```{r}
ggplot(final_df, aes(x=power2, y=edges)) +
  scale_x_log10() +
  geom_point() +
  labs(title = "Number of Edges")
```

The number of edges is descresing as the threshold increases


```{r}
ggplot(final_df, aes(x=power2, y=num_connect_comps)) +
  scale_x_log10() +
  geom_point() +
  labs(title = "Number of connected Components")
```
```{r}
df_peak <- year2010 %>%
  filter(num_email > 256)

g_peak <- graph_from_data_frame(df_peak, directed = FALSE, vertices = NULL)
num_connect_comps <- no.clusters(g_peak)
num_connect_comps
plot(g_peak, vertex.label=NA)
```




```{r}

next_df <- year2010 %>%
  filter(num_email > 516)

g_next <- graph_from_data_frame(next_df, directed = FALSE, vertices = NULL)
num_connect_comps <- no.clusters(g_next)
num_connect_comps
plot(g_next, vertex.label=NA)
```

```{r}
ggplot(final_df, aes(x=power2, y=percent_connect_comp)) +
  scale_x_log10() +
  geom_point() +
  labs(title = "Percent of the nodes in the largest connected component ")
```


```{r}
ggplot(final_df, aes(x=power2, y=avg_distance)) +
  scale_x_log10() +
  geom_point() +
  labs(title = "Average distance to get from one node to the next")
```