---
title: "HW2-Problem2"
author: "Devin Etcitty"
date: "4/4/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(modelr)
```

Read data

```{r}
data <- read_tsv('polyfit.tsv')
```

shuffle the data and assign each row to one of 5 different folds
make sure to use this seed
```{r}
set.seed(4990)

```


```{r}
data

```

```{r}
names(data)
```



```{r}
plot(data)
```

```{r}
ggplot(data, aes(x, y)) +
  geom_point()
```


implement 5-fold cross-validation to compute the average train / test error (RMSE) for each polynomial degree
```{r}
cv5 <- crossv_kfold(data, 5)
cv5
```

make a plot showing the how the train and test error vary with the polynomial degree
```{r}

cv5 %>% 
  mutate(train = map(train, as_tibble)) %>%
  mutate(model = map(train, ~ lm(y ~ x, data=.))) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>%
  select(.id, rmse)


```


```{r}
cv5 %>% 
  mutate(train = map(train, as_tibble)) %>%
  mutate(model = map(train, ~ lm(y ~ x + I(x)^2, data=.))) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>%
  select(.id, rmse)


```

```{r}
cv5 %>% 
  mutate(train = map(train, as_tibble)) %>%
  mutate(model = map(train, ~ as.formula(y ~ poly(x, 3, raw = T)), data=.)) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>%
  select(.id, rmse)
```


```{r}
K <- 20
form <- as.formula(y ~ poly(x, K, raw=T))
ddply(cv5, .(test, test), as.data.frame)
M <- model.matrix(form, model_data)
head(M)
```
```{r}
cv5_new <- cv5 %>%
  mutate(model = map(train, ~ as.formula( y ~ poly(x, K, raw=T)  ) ) )

cv5_new$model[[1]] %>% summary()
```



```{r}
K <- 1:30

coeff_all_models = matrix(0, ncol = 30, nrow = 0)

test <- cv5$train
train <- cv5$train

model = df
for (j in K) 
{
  
  for ( i in nrow(cv5))
  {
    one_train_df <- as.data.frame(test[i])
    sub_test_df <- as.data.frame(test[i])
    
    colnames(one_train_df) =c ("x", "y")
    colnames(sub_test_df) =c ("x", "y")
    
    form <- as.formula(y ~ poly(x, j, raw=T))
    M <- model.matrix(form, one_train_df)
    model <- lm(form, one_train_df)
    coefs <- (model$coefficients)
    blank <- integer(j)
    
    coeff_all_models[1] <- coefs

    #cbind(coeff_all_models, coefs)
    
  
  }
}
```



select the degree with the lowest average test error
```{r}
cv5_new$model

```

fit a final model for this degree on all of the data
```{r}

```


make a scatter plot of all of the data with the best-fit model overlayed as a line
```{r}

```

report the coefficients for the best-fit model
```{r}

```

